### 2016-06-07 abstract.tex
Some edits.

In this paper, we propose an operational model and a compositional
reasoning framework for concurrent imperative programs with weakly
isolated transactions (\txnimp programs, as we call them).  Our
operational model captures all the behaviors exhibited by a program
under weak isolation without referring to any specific implementation
of isolation. Our reasoning framework enables formal reasoning about
program invariants while taking into account the fine-grained
isolation semantics of transactions. We use a combination of simple
static analysis and manual proofs in our reasoning framework to
formally establish the correctness for several benchmarks, which were
hitherto known to be correct only through experiments.
\end{abstract}

>>>>

In this paper, we propose an operational model and a compositional
proof system for concurrent imperative programs with weakly isolated
transactions (\txnimp programs, as we call them).  Our operational
model captures all the behaviors exhibited by a program under weak
isolation without referring to any specific implementation of
isolation. Our proof system enables formal reasoning about program
invariants while taking into account the fine-grained isolation
semantics of transactions. Case studies demonstrate the utility of our
approach.
\end{abstract}
